Robust and Efficient CSI Compression Using CLLWCsiNet in Noisy MIMO Environments

### 2025-04-11 Revise-version.tex
Changing-Structure-Of-Paper Splitting the Imperfect channel into 3 section

@@

>>>>

\section{Channel Imperfections in CSI Feedback Systems}
\subsection{Noise Characteristics in Practical Scenarios}
[Move here: Initial 2 paragraphs about noise importance and Sun et al.'s limitations]
[Keep Figure \ref{fig:Performance of Models under the various noise power}]

\subsection{Mathematical Modeling of Imperfections}
[Move here: Your AWGN equations:
\begin{equation}
\tilde{S}=S+\textbf{n}
\end{equation}
\begin{equation}
\tilde{n}=g_{L}(...g_{1}(\tilde{S}))
\end{equation}]

\section{Analysis of Existing Denoising Approaches}
\subsection{DNNet Architecture Breakdown}
[Move here: DNNet description with equations:
\begin{equation}
\left\{
\begin{array}{ll}
	z  & \mbox{if } l=1 \\
	\zeta(W_{l}z+b_{l}) & \mbox{if } 2\le l \le L-1  \\
	W_{l}z+b_{l} & \mbox{if } l=L  
\end{array} 
\right.
\end{equation}]

\subsection{Limitations of Current Methods}
[Move here: Paragraphs about DNNet's parameter explosion and training complexity]
[Keep all critical observations about FC layers]

@@

\section{Proposed Denoising Framework}
\subsection{Architecture Design}
[Move here: Your federated learning approach description]
[Keep all details about noise power ranges (-5dB to 40dB)]

\subsection{Training Methodology}
[Move here: "To evaluate previous models...pretrained models" paragraph]
[Keep the convolutional latent space discussion]

\subsection{Performance Analysis}
[Move here: "As illustrated in Figure..." results discussion]
[Preserve all NMSE comparisons and 70K parameters note]
